# Composition

Stacked barplot is often used as a visualization way to display the microbial composition per sample.  

**Loading packages**

```R
library(XMAS)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
```


## Loading & precessing phyloseq object

Removing the spike-in sample
```{r, warning=FALSE, message=FALSE}
data("dada2_ps")
dada2_ps_without_QC <- get_GroupPhyloseq(
    ps = dada2_ps,
    group = "Group",
    group_names = "QC",
    discard = TRUE)
dada2_ps_without_QC
```


## Stacked barplot 

`plot_StackBarPlot` provides too many parameters for users to display the Stacked barplot of microbial composition by using ggplot2 format. Here is the ordinary pattern. More details to see `help(plot_StackBarPlot)`.

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=4, fig.cap="Stacked barplot Ordinary pattern"}
plot_StackBarPlot(
        ps=dada2_ps_without_QC,
        taxa_level="Phylum")
```


Please open the below buttons, if you want to see other options for stacked barplot.

<details>
<summary>**genus level in stacked barplot**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=7, fig.height=8, fig.cap="Stacked barplot otu_tab and sample_table as input"}
dada2_ps_without_QC_genus <- summarize_taxa(dada2_ps_without_QC, taxa_level = "Genus")
otu_tab <- phyloseq::otu_table(dada2_ps_without_QC_genus)
sam_tab <- phyloseq::sample_data(dada2_ps_without_QC_genus)
plot_StackBarPlot(
      data_otu=otu_tab,
      data_sam=sam_tab,
      taxa_level="Genus")
```
</details>


<details>
<summary>**Metadata with `Group` phenotype**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6.5, fig.height=7, fig.cap="Stacked barplot Metadata with group"}
plot_StackBarPlot(
        ps=dada2_ps_without_QC,
        taxa_level="Phylum",
        group = "Group")
```
</details>


<details>
<summary>**Metadata with `Group` phenotype in cluster mode**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6.5, fig.height=7, fig.cap="Stacked barplot Metadata with group in cluster mode"}
plot_StackBarPlot(
        ps=dada2_ps_without_QC,
        taxa_level="Phylum",
        group = "Group",
        cluster = TRUE)
```
</details>


<details>
<summary>**Metadata with `Group` phenotype in facet**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=7, fig.height=5, fig.cap="Stacked barplot Metadata with group in facet"}
plot_StackBarPlot(
        ps=dada2_ps_without_QC,
        taxa_level="Phylum",
        group = "Group",
        facet = TRUE)
```
</details>


## Heatmaps

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=7, fig.height=5, fig.cap="Heatmaps"}
plot_taxa_heatmap(dada2_ps_without_QC, 
                  taxa_level = "Phylum", 
                  cutoff = 1e-4, 
                  colors = c("black", "yellow"))
```


## Systematic Information
```{r}
sessionInfo()
```

