# Composition

Stacked barplot is often used as a visualization way to display the microbial composition per sample.  

**Loading packages**

```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
library(SummarizedExperiment)
```


## Loading & precessing phyloseq object

* Using `get_GroupPhyloseq` to remove some samples. For instance, removing the spike-in sample QC in Group column.

* Rarefying counts
```{r, warning=FALSE, message=FALSE}
dada2_ps_remove_BRS <- get_GroupPhyloseq(
                     ps = dada2_ps,
                     group = "Group",
                     group_names = "QC")
dada2_ps_rarefy <- norm_rarefy(dada2_ps_remove_BRS, size = 51181, rng_seed = 123)
dada2_ps_rarefy
```


## Stacked barplot 

`plot_StackBarPlot` provides too many parameters for users to display the Stacked barplot of microbial composition by using ggplot2 format. Here is the ordinary pattern. More details to see `help(plot_StackBarPlot)`.

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=4, fig.cap="Stacked barplot Ordinary pattern"}
plot_StackBarPlot(ps=dada2_ps_rarefy, taxa_level="Phylum")
```


Please open the below buttons, if you want to see other options for stacked barplot.

<details>
<summary>**genus level in stacked barplot**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=7, fig.height=8, fig.cap="Stacked barplot otu_tab and sample_table as input"}
dada2_ps_rarefy_genus <- summarize_taxa(dada2_ps_rarefy, taxa_level = "Genus")
otu_tab <- phyloseq::otu_table(dada2_ps_rarefy_genus)
sam_tab <- phyloseq::sample_data(dada2_ps_rarefy_genus)
plot_StackBarPlot(
      data_otu=otu_tab,
      data_sam=sam_tab,
      cutoff = 0.01,
      taxa_level="Genus")
```
</details>


<details>
<summary>**Metadata with `Group` phenotype**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6.5, fig.height=7, fig.cap="Stacked barplot Metadata with group"}
plot_StackBarPlot(
        ps=dada2_ps_rarefy,
        taxa_level="Phylum",
        group = "Group")
```
</details>


<details>
<summary>**Metadata with `Group` phenotype in cluster mode**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6.5, fig.height=7, fig.cap="Stacked barplot Metadata with group in cluster mode"}
plot_StackBarPlot(
        ps=dada2_ps_rarefy,
        taxa_level="Phylum",
        group = "Group",
        cluster = TRUE)
```
</details>


<details>
<summary>**Metadata with `Group` phenotype in facet**</summary>
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=7, fig.height=5, fig.cap="Stacked barplot Metadata with group in facet"}
plot_StackBarPlot(
        ps=dada2_ps_rarefy,
        taxa_level="Phylum",
        group = "Group",
        facet = TRUE)
```
</details>


## XVIZ `plot_stacked_bar`

`plot_stacked_bar` from XVIZ.

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=6, fig.cap="Stacked barplot XVIZ"}
plot_stacked_bar_XIVZ(phyloseq=dada2_ps_rarefy, level="Phylum")
```

## Heatmaps

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=7, fig.height=5, fig.cap="Heatmaps"}
plot_taxa_heatmap(dada2_ps_rarefy, 
                  taxa_level = "Phylum", 
                  cutoff = 1e-4, 
                  colors = c("black", "yellow"))
```


## Systematic Information
```{r}
sessionInfo()
```
