# Core microbiota

These functions in this chapter are from [@microbiome] package. The core microbiota are passed the parameters' cutoff (eg. prevalence, abundance). 

**Loading packages**

```R
library(XMAS)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
```

## Core microbiota anlaysis

* Using `get_GroupPhyloseq` to remove some samples. For instance, removing the spike-in sample QC in Group column.

* Rarefying counts

* Genus data are from previous chapter and we will use this object
```{r, warning=FALSE, message=FALSE}
dada2_ps_remove_BRS <- get_GroupPhyloseq(
                     ps = dada2_ps,
                     group = "Group",
                     group_names = "QC")
dada2_ps_rarefy <- norm_rarefy(dada2_ps_remove_BRS, size = 51181, rng_seed = 123)

dada2_ps_rarefy_genus <- summarize_taxa(dada2_ps_rarefy, taxa_level = "Genus")
```

* Normalization: See the Chapter 6 Pre-processing
```{r, warning=FALSE, message=FALSE}
dada2_ps_rarefy_genus_rb <- normalize(dada2_ps_rarefy_genus, method = "TSS")
dada2_ps_rarefy_genus_rb
```


* Check for the core ASVs

Use `core_members` to obtain the core taxa. _detection_ for abundance and _prevalence_ for occurrence.
```{r, warning=FALSE, message=FALSE}
core_taxa_name <- core_members(dada2_ps_rarefy_genus_rb, detection = 0.01, prevalence = 0.8)
print(core_taxa_name)
```

**Result:**

Only **three** genera (g__Bifidobacterium, g__Blautia and g__Lachnospiraceae_unclassified) passed the threshold of detection and prevalence which we choose.


## Core abundance and diversity

Total core abundance in each sample (sum of abundances of the core members):

```{r, warning=FALSE, message=FALSE}
core_abundance <- sample_sums(phyloseq_core_taxa(dada2_ps_rarefy_genus_rb, detection = 0.01, prevalence = 0.8))

DT::datatable(data.frame(core_abundance))
```


## Core visualization

We display the taxa based on the prevalence and detection via two ways (heatmap or linechart plot).

### heatmap

* Core with composition
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="Core with composition in Heatmap"}
prevalences <- seq(0.05, 1, 0.05)
detections <- 10^seq(log10(1e-3), log10(.2), length = 10)

pl_core <- plot_core_taxa(dada2_ps_rarefy_genus_rb, 
                    plot.type = "heatmap", 
                    colours = gray(seq(0, 1, length=5)),
                    prevalences = prevalences, 
                    detections = detections, 
                    min.prevalence = 0.5)+
    xlab("Detection Threshold (Relative Abundance (%))")

pl_core
```

The degree of color indicates the size of abundance and prevalence.


* other colors: viridis
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="Core with composition in Heatmap (viridis)"}
library(viridis)
print(pl_core + scale_fill_viridis())
```

* change color
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="Core with composition in Heatmap (RColorBrewer)"}
library(RColorBrewer)

prevalences <- seq(0.05, 1, 0.05)
detections <- 10^seq(log10(1e-3), log10(.2), length = 10)

pl_core <- plot_core_taxa(dada2_ps_rarefy_genus_rb, 
                    plot.type = "heatmap", 
                    colours = rev(brewer.pal(5, "Spectral")),
                    prevalences = prevalences, 
                    detections = detections, 
                    min.prevalence = 0.5)+
    xlab("Detection Threshold (Relative Abundance (%))") +
    theme(axis.text.y = element_text(face="italic"))

pl_core
```


### linechart

This plot show the relationship between Detection and Prevalence in a linear model.

```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=5, fig.height=4, fig.cap="Core with composition in linechart"}
prevalences <- seq(0.05, 1, 0.05)
detections <- 10^seq(log10(1e-3), log10(.2), length = 10)

pl_core <- plot_core_taxa(dada2_ps_rarefy_genus_rb, 
                    plot.type = "lineplot", 
                    prevalences = prevalences, 
                    detections = detections, 
                    min.prevalence = 0.5)+
    xlab("Detection Threshold (Relative Abundance (%))") +
    theme(axis.text.y = element_text(face="italic"))

pl_core
```


When increasing the Detection, the core size turns to low level.


## Systematic Information
```{r}
sessionInfo()
```

