# Visualization

**XMAS 2.0** provides functions for visualization.

**Loading packages**
```{r, echo=TRUE, results="hide", warning=FALSE, message=FALSE}
library(XMAS2)
library(dplyr)
library(tibble)
library(phyloseq)
library(ggplot2)
library(ggpubr)
library(SummarizedExperiment)
```

## plot_boxplot

```{r, warning=FALSE}
data("amplicon_ps")
dat_alpha <- run_alpha_diversity(ps=amplicon_ps, measures = c("Shannon", "Chao1", "Observed"))
head(dat_alpha)
```

`plot_boxplot` has many parameters, and help you enjoy it.

* single measure 
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="boxplot(single measure)"}
plot_boxplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = FALSE)
```

* single measure with significant results
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="boxplot(single measure with significant results)"}
plot_boxplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE)
```

* single measure with significant results of pairwises
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="boxplot(single measure with significant results of pairwises)"}
plot_boxplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             cmp_list = list(c("gut", "right palm"), c("gut", "tongue")))
```

* single measure with significant results of pairwises and outlier
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="boxplot(single measure with significant results of pairwises and outlier)"}
plot_boxplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             cmp_list = list(c("gut", "right palm"), c("gut", "tongue")),
             outlier = TRUE)
```

* single measure with significant results of ref_group
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="boxplot(single measure with significant results of ref_group)"}
plot_boxplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             ref_group = "gut")
```

* multiple measures
```{r, warning=FALSE, fig.width=9, fig.height=5, fig.align="center", fig.cap="boxplot(multiple measure with group number)"}
plot_boxplot(data=dat_alpha,
             y_index = c("Shannon", "Chao1", "Observed"),
             group = "SampleType",
             group_names = c("gut", "right palm", "tongue"),
             group_color = c("red", "green", "blue"),
             ref_group = "gut",
             method = "wilcox.test",
             outlier = TRUE)
```



## plot_barplot

`plot_barplot` has many parameters, and help you enjoy it.


* single measure 
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="barplot(single measure)"}
plot_barplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = FALSE)
```

* single measure with significant results
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="barplot(single measure with significant results)"}
plot_barplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE)
```

* single measure with significant results of pairwises
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="barplot(single measure with significant results of pairwises)"}
plot_barplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             cmp_list = list(c("gut", "right palm"), c("gut", "tongue")))
```

* single measure with significant results of ref_group
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="barplot(single measure with significant results of ref_group)"}
plot_barplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             ref_group = "gut")
```

* multiple index
```{r, warning=FALSE, fig.width=8, fig.height=4, fig.align="center", fig.cap="barplot(multiple index)"}
plot_barplot(data=dat_alpha,
              y_index=c("Shannon", "Chao1", "Observed"),
              group="SampleType",
              do_test=TRUE,
              method="wilcox.test")
```



## plot_dotplot

`plot_dotplot` has many parameters, and help you enjoy it.

* single measure 
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="dotplot(single measure)"}
plot_dotplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = FALSE)
```

* single measure with significant results
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="dotplot(single measure with significant results)"}
plot_dotplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE)
```

* single measure with significant results of pairwises
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="dotplot(single measure with significant results of pairwises)"}
plot_dotplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             cmp_list = list(c("gut", "right palm"), c("gut", "tongue")))
```


* single measure with significant results of ref_group
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="dotplot(single measure with significant results of ref_group)"}
plot_dotplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             ref_group = "gut")
```


* dot size and median size
```{r, warning=FALSE, fig.width=6, fig.height=5, fig.align="center", fig.cap="dotplot(dot size and median size)"}
plot_dotplot(data=dat_alpha,
             y_index = "Shannon",
             group = "SampleType",
             do_test = TRUE,
             ref_group = "gut",
             dotsize = 0.5,
             mediansize = 2)
```

* multiple index
```{r, warning=FALSE, fig.width=8, fig.height=4, fig.align="center", fig.cap="dotplot(multiple index)"}
plot_dotplot(data=dat_alpha,
              y_index=c("Shannon", "Chao1", "Observed"),
              group="SampleType",
              do_test=TRUE,
              method="wilcox.test")
```


* multiple index with errorbar
```{r, warning=FALSE, fig.width=8, fig.height=4, fig.align="center", fig.cap="dotplot(multiple index errorbar)"}
plot_dotplot(data=dat_alpha,
              y_index=c("Shannon", "Chao1", "Observed"),
              group="SampleType",
              do_test=TRUE,
              show_type="errorbar",
              method="wilcox.test")
```



## plot_correlation_boxplot

Help you enjoy `plot_correlation_boxplot`.
```{r, warning=FALSE, fig.width=8, fig.height=6, fig.align="center", fig.cap="correlation with boxplot"}
plot_correlation_boxplot(data=dat_alpha,
             x_index="Chao1",
             y_index="Shannon",
             group="SampleType")
```


## plot_correlation_density

Help you enjoy `plot_correlation_density`.
```{r, warning=FALSE, fig.width=8, fig.height=6, fig.align="center", fig.cap="correlation with density"}
plot_correlation_density(data=dat_alpha,
             x_index="Chao1",
             y_index="Shannon",
             group="SampleType")
```


## plot_Ordination

`plot_Ordination` provides too many parameters for users to display the ordination results by using ggplot2 format. Here is the ordinary pattern.

```{r, warning=FALSE, message=FALSE}
data("dada2_ps")

# step1: Removing samples of specific group in phyloseq-class object
dada2_ps_remove_BRS <- get_GroupPhyloseq(
                     ps = dada2_ps,
                     group = "Group",
                     group_names = "QC")

# step2: Rarefying counts in phyloseq-class object
dada2_ps_rarefy <- norm_rarefy(dada2_ps_remove_BRS, size = 51181, rng_seed = 123)

# step3: Extracting specific taxa phyloseq-class object 
dada2_ps_rare_genus <- summarize_taxa(dada2_ps_rarefy, taxa_level = "Genus", absolute = TRUE)

# step4: Aggregating low relative abundance or unclassified taxa into others
#dada2_ps_genus_LRA <- summarize_LowAbundance_taxa(dada2_ps_rare_genus, cutoff = 10, unclass = TRUE)

# step4: Filtering the low relative abundance or unclassified taxa by the threshold
dada2_ps_genus_filter <- run_filter(dada2_ps_rare_genus, cutoff = 10, unclass = TRUE)

# step5: Trimming the taxa with low occurrence less than threshold
dada2_ps_genus_filter_trim <- run_trim(dada2_ps_genus_filter, cutoff = 0.2, trim = "feature")
dada2_ps_genus_filter_trim

ordination_PCA <- run_ordination(
                       ps = dada2_ps_genus_filter_trim,
                       group = "Group",
                       method = "PCA")

names(ordination_PCA)
```

* Ordinary pattern
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=6, fig.cap="plot_Ordination (Ordinary pattern)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group")
```


* plot with SampleID and setting group colors
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=6, fig.cap="plot_Ordination (Ordinary pattern with SampleID)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse",
                sample = TRUE)
```


* ellipse with 95% confidence interval
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=6, fig.cap="plot_Ordination (ellipse with 95% confidence interval)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse_CI",
                sample = TRUE)
```


* ellipse with groups
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=6, fig.cap="plot_Ordination (ellipse with groups)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse_groups",
                sample = TRUE)
```


* ellipse with border line
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=8, fig.height=6, fig.cap="plot_Ordination (ellipse with border line)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse_line",
                sample = TRUE)
```


* plot with SampleID and sideboxplot and setting group colors
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="plot_Ordination (Ordinary pattern with SampleID sideboxplot)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse",
                sidelinechart = FALSE,
                sideboxplot = TRUE,
                sample = TRUE)
```


* plot with SampleID and sideboxplot and setting group colors 2
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="plot_Ordination (ellipse_CI with SampleID sideboxplot)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse_CI",
                sidelinechart = FALSE,
                sideboxplot = TRUE,
                sample = TRUE)
```


* plot with SampleID and sideboxplot and setting group colors 3
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="plot_Ordination (ellipse_groups with SampleID sideboxplot)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse_groups",
                sidelinechart = FALSE,
                sideboxplot = TRUE,
                sample = TRUE)
```


* plot with SampleID and sideboxplot and setting group colors 4
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="plot_Ordination (ellipse_line with SampleID sideboxplot)"}
plot_Ordination(ResultList = ordination_PCA, 
                group = "Group", 
                group_names = c("AA", "BB"),
                group_color = c("blue", "red"),
                circle_type = "ellipse_line",
                sidelinechart = FALSE,
                sideboxplot = TRUE,
                sample = TRUE)
```


* plot with SampleID and sideboxplot and setting group colors and shape
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="plot_Ordination (ellipse_line with SampleID sideboxplot)"}
data("amplicon_ps")
amplicon_ps_genus <- summarize_taxa(amplicon_ps, taxa_level = "Genus")
amplicon_res_ordination <- run_ordination(
                      ps = amplicon_ps_genus,
                      group = "SampleType",
                      method = "PCoA")

plot_Ordination(ResultList = amplicon_res_ordination, 
                group = "SampleType",
                shape_column = "ReportedAntibioticUsage",
                shape_values = c(16, 17),
                circle_type = "ellipse_line",
                sidelinechart = FALSE,
                sideboxplot = TRUE,
                sample = TRUE)
```

## plot_ggbiplot

* biplot with topN dominant taxa
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=5, fig.cap="plot_ggbiplot (biplot)"}
plot_ggbiplot(ResultList = ordination_PCA,
              group = "Group",
              group_color = c("blue", "red"),
              topN = 5,
              ellipse = TRUE,
              labels = "SampleID")
```


## plot_corrplot
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="plot_corrplot (distance)"}
dada2_beta <- run_beta_diversity(ps=dada2_ps_rarefy, method = "bray")
plot_distance_corrplot(dada2_beta$BetaDistance)
```


## plot_2DA_venn
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=6, fig.cap="plot_2DA_venn (wilcox vs t_test)"}
da_wilcox <- run_wilcox(dada2_ps_genus_filter_trim,
                     group = "Group",
                     group_names = c("AA", "BB"))

da_ttest <- run_ttest(dada2_ps_genus_filter_trim,
                     group = "Group",
                     group_names = c("AA", "BB"))

DA_venn_res <- plot_2DA_venn(
         daTest1 = da_wilcox,
         daTest2 = da_ttest,
         datType1 = "AA vs BB(wilcox)",
         datType2 = "AA vs BB(t-test)",
         group_names = c("AA", "BB"),
         Pvalue_name = "Pvalue",
         logFc_name1 = "Log2FoldChange (Rank)\nAA_vs_BB",
         logFc_name2 = "Log2FoldChange (geometricmean)\nAA_vs_BB",
         Pvalue_cutoff = 0.8,
         logFC_cutoff = 0.2)
DA_venn_res$pl
```


## plot the DA results from the significant taxa by double barplot
```{r, warning=FALSE, fig.align="center", fig.width=7, fig.height=5, fig.cap="double barplot for DA results"}
data("amplicon_ps")
DA_res <- run_wilcox(amplicon_ps, taxa_level="Family", group="SampleType", group_names=c("tongue", "gut"))

plot_double_barplot(data=DA_res,
              x_index="Log2FoldChange (Rank)\ntongue_vs_gut",
              x_index_cutoff=1,
              y_index="AdjustedPvalue",
              y_index_cutoff=0.05)
```

## plot_stacked_bar_XIVZ

* Minimum usage: plot in relative abundance
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=12, fig.height=6, fig.cap="plot_stacked_bar_XIVZ (test1)"}
plot_stacked_bar_XIVZ(phyloseq = dada2_ps_rarefy, level = "Family")
```


* Set feature parameter to show feature information
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=12, fig.height=8, fig.cap="plot_stacked_bar_XIVZ (test2)"}
plot_stacked_bar_XIVZ(phyloseq = dada2_ps_rarefy, 
                 level = "Family",
                 feature = "Group")
```

* Pass ordered sample names to order parameter to plot in specific order
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=12, fig.height=8, fig.cap="plot_stacked_bar_XIVZ (test3)"}
metadata <- phyloseq::sample_data(dada2_ps_rarefy) %>% 
  data.frame() %>%
  dplyr::arrange(Group)
plot_stacked_bar_XIVZ(phyloseq = dada2_ps_rarefy, 
                 level = "Family",
                 feature = "Group",
                 order = rownames(metadata))
```


* Use facet_wrap(vars(), scale="free") funciton to facet stacked barplot
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=12, fig.height=8, fig.cap="plot_stacked_bar_XIVZ (test4)"}
plot_stacked_bar_XIVZ(phyloseq = dada2_ps_rarefy, 
                 level = "Family", 
                 relative_abundance = TRUE, 
                 order = rownames(metadata)) + 
  facet_wrap(vars(Group), scale="free")
```


## plot_StackBarPlot 

`plot_StackBarPlot` provides too many parameters for users to display the Stacked barplot of microbial composition by using ggplot2 format. Here is the ordinary pattern. More details to see `help(plot_StackBarPlot)`.

* Ordinary pattern
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6, fig.height=4, fig.cap="plot_StackBarPlot(Ordinary pattern)"}
plot_StackBarPlot(ps=dada2_ps_rarefy, taxa_level="Phylum")
```

* Metadata with `Group` phenotype
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6.5, fig.height=7, fig.cap="plot_StackBarPlot (Metadata with group)"}
plot_StackBarPlot(
        ps=dada2_ps_rarefy,
        taxa_level="Phylum",
        group = "Group")
```


* Metadata with `Group` phenotype in cluster mode
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=6.5, fig.height=7, fig.cap="plot_StackBarPlot (Metadata with group in cluster mode)"}
plot_StackBarPlot(
        ps=dada2_ps_rarefy,
        taxa_level="Phylum",
        group = "Group",
        cluster = TRUE)
```

* Metadata with `Group` phenotype in facet
```{r, warning=FALSE, message=FALSE, fig.align="center", fig.width=7, fig.height=5, fig.cap="plot_StackBarPlot (Metadata with group in facet)"}
plot_StackBarPlot(
        ps=dada2_ps_rarefy,
        taxa_level="Phylum",
        group = "Group",
        facet = TRUE)
```


## Systematic Information
```{r}
devtools::session_info()
```
